\section*{Acknowledgement}
I would like to express my appreciation to \emph{Dr. Reiko Tanaka} for her generous help in reviewing these notes with the highest profession.
\ \\ \\
I would like to extent my thanks to \emph{Ashira Meyer}, \emph{Aron Lajko}, \emph{Daniel Duffill}, \emph{Kenny Panteleev}, \emph{Peter Xie}, \emph{Weixun Luo} and \emph{rep group} for their insightful comments and suggestions that have continuously improved this note. Their work significantly optimized the structure. 
\ \\ \\
Special thanks to \emph{Haroon Chughtai}. His notes greatly enlightened me when preparing this new set.

%========================================================
\section*{Errata}
Colors are used to code different actions applied to the context. {\color{blue}blue} is used for replacement, {\color{red}red} for removal, and {\color{green}green} for addition.

\paragraph{8\textsuperscript{th} Mar 2024}
\begin{itemize}
    \item \textit{Section 2, Example 2.1} Two typos have been corrected. On page 8:
    \[ 
        y(t) = g(t) = \mathcal{L}^{-1} [G(s)] = -e^{-t/2}+{\color{red}-}e^{-t/3} 
    \]
    \[ 
        y(t) = 2e^{-t/2}-3{\color{green}e}^{-t/3} +1 
    \]

    \item \textit{Section 6.6} \quad A typo has been corrected. On page 31: 
    \begin{center}
        The phase plot at $-90^{\circ}$ at $r = r_c = {\color{blue}1}$. 
    \end{center}
\end{itemize}

\paragraph{16\textsuperscript{th} Mar 2021}
\begin{itemize}
    \item \textit{Section 3.1.1} \quad Added the missing bracket in the expression of $b_{i}^{(k)}$.
    \item \textit{Section 3.2} \quad The typos $t \to 0$ in the expression of final value theorem and the example below has been fixed. 
    \item \textit{Section 6.3} \quad Fixed the wrong legend. The legend in the Bode plot of $(\frac{1}{s})^{n}$ should start from $n=0$.
    \item \textit{Section 8.2.4} \quad Fixed the typo in the example. The second solution should be  $k_{2}$.
\end{itemize}

\paragraph{14\textsuperscript{th} Mar 2021}
\begin{itemize}
    \item \textit{Section 1.1 \& 1.2} \quad I have changed the bullet points to tables.
    \item \textit{Section 8.1} \quad The typo in the transfer function has been fixed.
\end{itemize}

\section*{Source File}
\faGithub \ click to access the GitHub repository for \href{https://github.com/binghuan-li/Notes-and-Formula-Sheets}{this document}.