\section*{Preface, Rationale, \& Acknowledgement}
These notes are compiled based on the lectures of \textit{Digital Biosignal Processing} delivered by \textit{Professor Dario Farina} at the Department of Bioengineering, Imperial College London during September-December 2021. Additional examples were adopted and/or inspired by various educational sources, including the notes on Digital Signal Processing by \textit{Dr Aidan Hogg} (Imperial), recordings of Signals and Systems by \textit{Professor Alan Oppenheim} (MIT), and notes on Signals and Systems by \textit{Dr Michael Adams} (University of Victoria). \\

I began drafting this document in 2021, completing the drafts for the first four sections by the summer of 2022. The subsequent sections were drafted raggedly in December 2022, June 2023, and December 2023, with the final proofreading completed in November 2024. It has been quite some time since my undergraduate years, and given that my current research focus is relatively distant from signal processing applications, I am less certain about the practical usefulness of this document. However, what remains clear is that this document takes me back to that bittersweet autumn of 2021 - Uren L9, RSM 335, unsolvable MiB coursework, and loads (!) of \texttt{MATLAB} exercises.\\

Note that this document is still in its beta version (Nov. 2024). A few chapters are pending to be proofread and improved.

\faGithub \ The \LaTeX \ files are now accessible on my \href{https://github.com/binghuan-li/Notes-and-Formula-Sheets}{GitHub repository}. I hope it helps. Please report typos and inconsistencies to \href{mailto:binghuan.li19@imperial.ac.uk}{binghuan.li19@imperial.ac.uk}. \\

\textit{To my undergraduate years.}

\begin{flushright}
November, 2024\\
London, UK
\end{flushright}

\vfill
{\color{gray}
Cover image: Signal Processing Workflow: From Analog to Digitally Filtered Outputs, reproduced based on a figure from the lecture notes by \textit{Robert F. Port}.
}